Zero-Knowledge Credentials for Smart Contracts

### 2018-05-14 paper/paper.tex
Spelling error

\subsubsection{Credential Annotated ABI}
The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
The required annotations describe the required credentials for a given method within the smart contract and will
be used to propery construct public inputs and subsequently generate proofs for credentials. An annotated ABI function
would appear as follow:
\begin{lstlisting}

  {"constant":false,
   "name":"Join",
   "inputs":[],
   "outputs":[],
   "payable":false,
   "type":"function","
    "credentials":[
      {"contract_salt":"0xdeadbeef",
      "high_bound":255,
      "low_bound":18,
      "k_bound":1,
      "description": "Confirms holder is over 18."
      }
    ]
  }
\end{lstlisting}

@@

To utlize the framework a dApp simply replaces all existing contract calls with calls to their credential accepting counterparts. 
This can be accomplished very concisely by wrapping the credial-accepting method call with partially applied
function. A full implementation of this exists in our example application and is depicted in [INSERT FIG NUMBER];
\begin{lstlisting}
function OnJoinClick() {
  var credBlock = new CredentialBlock("Join", PartialAppJoin(), lottery_abi);
    credBlock.display();
}

function PartialAppJoin(/* Insert non-proof arguments here*/) {
  return function (proof_bytes) {
    contractInstance.methods["Join"](/* Non-Proof Arguments*/ ,proof_bytes).send();
  }
}

\end{lstlisting}

In the above example, "Join" allowed a users to join a lottery if they have the required credentials. Originally, took a number of non-proof arguments. 
The credential enabled join now takes the non-proof arguments as well as proof arguments. This partial application hides the non-proof arguments from the ZKID CredentialBlock and allows the CredentialBlock to 
supply the proof arguments post proof-generation. The dApp's code has now migrated its call to "Join" to a credential-enabled call with minimal additions.

>>>>

\subsubsection{Credential Annotated ABI}
The properly interface with the ZKID Service a dApp would provide an annotated ABI for its dependant contract(s).
The annotations describe the required credentials for a given method within the smart contract and will
be used to communicate public inputs to the ZKID prooving service. An annotated ABI function
would appear as follow:

@@

To utlize the framework a dApp simply replaces all existing contract calls with calls to their credential accepting counterparts. 
This can be accomplished very concisely by wrapping the credial-accepting method call with partially applied
function.

The "Join" function in the provided example application is an example of how to properly provide the ZKID framework with a partially applied credential-enabled function. Originally, took a number of non-proof arguments. 
The credential enabled join now takes the non-proof arguments as well as proof arguments. This partial application hides the non-proof arguments from the ZKID CredentialBlock and allows the CredentialBlock to 
supply the proof arguments post proof-generation. The dApp's code has now migrated its call to "Join" to a credential-enabled call with minimal additions.
